---
title: "Experiment Pipeline for the Experiment on the Relationship Between the Illusion of Causality and the Foreign Language Effect"
output: pdf_document
date: "2025-03-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This `R` code is used to extract variables from raw participant sheet data. Only these data will be analyzed ultimately.

## Importing the File with Variables

First, we select the `ExperimentVariables.csv` file as the one we intend to use to guide the extraction of data. This file is available on the [**OSF project webpage**](https://osf.io/hvgkx/?view_only=7098178875224cf3b0b6890b209432ea) (this webpage link is in read-only mode for peer review purposes) for this study.

```{r carsu}
#Choose "ExperimentVariables.csv"
# coordinate <- read.csv(file.choose())
```

## Function to Extract Raw Data

This function extracts raw data to compose the final dataset to use. The commented-out code can be uncommented to specify the working directory (`setwd()`) containing the experiment raw data.

```{r cars}
estrai_valori <- function(file_path) {
  dataset <- read.csv(file_path)
  
  risultati <- c()
  
  variabili <- coordinate[, 2]  # The column for the variables names
  
  righe <- coordinate[, 4]  # The rows to extract
  
  for (i in 1:length(variabili)) {
    var <- variabili[i]
    if (var %in% colnames(dataset)) {
      risultati <- c(risultati, dataset[righe[i], var])
    } else {
      risultati <- c(risultati, NA)
    }
  }
  
  return(risultati)
}

# setwd("your_directory_path")  # Uncomment to specify working directory
# file_paths <- list.files(getwd())  # Uncomment to list files in working directory

```

```{r carsuc, echo=FALSE}
 coordinate <- read.csv("/Users/stefanodallabona/Desktop/Materials CLTFLE/Variabili Esperimento/ExperimentVariables.csv")
file_paths <- list.files("/Users/stefanodallabona/Desktop/Materials CLTFLE/PipelineandPilot/PilotData")
file_paths <- c("/Users/stefanodallabona/Desktop/Materials CLTFLE/PipelineandPilot/PilotData/pilot_participant_CLTandFLE_2025-03-25_14h50.55.328.csv","/Users/stefanodallabona/Desktop/Materials CLTFLE/PipelineandPilot/PilotData/pilot_participant_CLTandFLE_2025-03-25_14h35.21.956.csv")
                

```

## Extracting Raw Data to Create a Dataframe

We give an example with a few pilot data used to test the experiment:

```{r carsu8o}
risultati <- lapply(file_paths, estrai_valori)

df_risultati <- do.call(rbind, risultati)

# Assign column names based on the coordinate file
colnames(df_risultati) <- coordinate[, 3]  

df_risultati <- as.data.frame(df_risultati)

df_risultati
```
